---
title: "DEGs"
author: "Maggie Schedl"
date: "6/24/2020"
output: github_document
---


```{r}
#libraries
library(naniar)
library(tidyverse)
library(dplyr)
library(stringr)
```

Read i orthogroups file and do same file manipulations as in annotation script
```{r}
orthologs <- read.delim("LORF_EL90.pep__v__SPU_peptide.tsv", sep = "\t")
head(orthologs)
EL.orthologs <- orthologs %>% 
  select(1,2)
head(EL.orthologs)
# collapse df in to one column multiple rows instead of one row multiple columns
tr.orthogroups <- separate_rows(EL.orthologs, "LORF_EL90.pep", sep = ",", convert = FALSE)
head(tr.orthogroups)
# remove extra characters of .p#s
tr.orthogroups <-mapply(gsub, pattern = ".p1", replacement = "", tr.orthogroups)
tr.orthogroups <- as.data.frame(tr.orthogroups)
# I don't know why this always removes the column names but it does
# remove .p2
tr.orthogroups <-mapply(gsub, pattern = ".p2", replacement = "", tr.orthogroups)
tr.orthogroups <- as.data.frame(tr.orthogroups)
# remove .p3
tr.orthogroups <-mapply(gsub, pattern = ".p3", replacement = "", tr.orthogroups)
tr.orthogroups <- as.data.frame(tr.orthogroups)
# remove .p4
tr.orthogroups <-mapply(gsub, pattern = ".p4", replacement = "", tr.orthogroups)
tr.orthogroups <- as.data.frame(tr.orthogroups)
# remove .p5
tr.orthogroups <-mapply(gsub, pattern = ".p5", replacement = "", tr.orthogroups)
tr.orthogroups <- as.data.frame(tr.orthogroups)
# add column names
colnames(tr.orthogroups) <- c("Orthogroup", "transcript_id")
head(tr.orthogroups)
```

read in SPU annotation file with the orthogroups label in it

```{r}
annot.ortho.SPU <- read.delim("annot.ortho.SPU.txt", sep = "\t")
head(annot.ortho.SPU)

```

read in lists of DEGS 

```{r}
sig_LH_LA <- read.delim("sig_LH_LA.txt", sep = "\t")
head(sig_LH_LA)
sig_BH_BA <- read.delim("sig_BH_BA.txt", sep = "\t")
head(sig_BH_BA)
sig_GH_GA <- read.delim("sig_GH_GA.txt", sep = "\t")
head(sig_GH_GA)
```

What are the orthogroups of the DEGs?
```{r}
# give it the column to merge by
sig_LH_LA$transcript_id <- rownames(sig_LH_LA)
head(sig_LH_LA)
# make dataframe of only LH_LA sig othrogroups
LH_LA_orthogroups <- merge(sig_LH_LA, tr.orthogroups, by= "transcript_id", sort = TRUE )
head(LH_LA_orthogroups)
# ok this is nothing because the orthogroup file is all by isoforms not genes

```

I think what I'll need to do is just remove the _i# and then remove the duplicate rows...

```{r}
# I can use . as any character! 
tr.orthogroups.genes <-mapply(gsub, pattern = "_i.", replacement = "", tr.orthogroups)
tr.orthogroups.genes <- as.data.frame(tr.orthogroups.genes)
# there might be random spaces in the file??
tr.orthogroups.genes <-mapply(gsub, pattern = " ", replacement = "", tr.orthogroups.genes)
tr.orthogroups.genes <- as.data.frame(tr.orthogroups.genes)
colnames(tr.orthogroups.genes) <- c("Orthogroup", "transcript_id")
tr.orthogroups.genes.d <- unique(tr.orthogroups.genes)

tr.orthogroups.genes[1:100,]
tr.orthogroups.genes.d[1:100,]


```

```{r}
sig_LH_LA$transcript_id <- rownames(sig_LH_LA)
LH_LA_orthogroups <- merge(sig_LH_LA, tr.orthogroups.genes.d, by= "transcript_id", sort = TRUE )
head(LH_LA_orthogroups)
sig_BH_BA$transcript_id <- rownames(sig_BH_BA)
sig_BH_BA_orthogroups <- merge(sig_BH_BA, tr.orthogroups.genes.d, by= "transcript_id", sort = TRUE )
head(sig_BH_BA_orthogroups)
sig_GH_GA$transcript_id <- rownames(sig_GH_GA)
sig_GH_GA_orthogroups <- merge(sig_GH_GA, tr.orthogroups.genes.d, by= "transcript_id", sort = TRUE )
head(sig_GH_GA_orthogroups)

```

remove the stats from the DEG lists

```{r}
sig_GH_GA_orthogroup <- sig_GH_GA_orthogroups %>% select(1,8)
head(sig_GH_GA_orthogroup) #29
sig_BH_BA_orthogroup <- sig_BH_BA_orthogroups %>% select(1,8)
head(sig_BH_BA_orthogroup)
dim(sig_BH_BA_orthogroup) #138 DEGS 
LH_LA_orthogroup <- LH_LA_orthogroups %>% select(1,8)
head(LH_LA_orthogroup) #3
```


Look for the orthogroups from the DEG lists in the annotation file that's merged with orthogroups.
```{r}
# blastula comparison 
Borthogroups <- sig_BH_BA_orthogroup$Orthogroup

Blastula_temp_DEG_annot <- subset(annot.ortho.SPU, Orthogroup %in% Borthogroups)
dim(Blastula_temp_DEG_annot) # 140 
# this is looking good that there are actually more, because there should be a few orthogroups with 2 genes
Blastula_temp_DEG_annot[1:10,]

# gastrula comparison
Gorthogroups <- sig_GH_GA_orthogroup$Orthogroup
Gastrula_temp_DEG_annot <- subset(annot.ortho.SPU, Orthogroup %in% Gorthogroups)
Gastrula_temp_DEG_annot[1:10,]
dim(Gastrula_temp_DEG_annot)

# larvae comparison
Lorthogroups <- LH_LA_orthogroup$Orthogroup
Larvae_temp_DEG_annot <- subset(annot.ortho.SPU, Orthogroup %in% Lorthogroups)
head(Larvae_temp_DEG_annot)



write.csv(Blastula_temp_DEG_annot,"Blastula_temp_DEG_annot.csv",col.names=TRUE,row.names=TRUE,sep=",")
write.csv(Gastrula_temp_DEG_annot,"Gastrula_temp_DEG_annot.csv",col.names=TRUE,row.names=TRUE,sep=",")
write.csv(Larvae_temp_DEG_annot,"Larvae_temp_DEG_annot.csv",col.names=TRUE,row.names=TRUE,sep=",")
```


GRN
some of the gene names had / in them to delimiate two gene names I think pertaining to the same gene
I separated them out into separate lines 
```{r}
GRN <- read.csv("journal.pbio.1002391.s013.GRN.csv", header = TRUE)
head(GRN)
dim(GRN) #126
```
Hopefully these are the same common names as in the annotation file...


Start with Blastula because it has the most...
```{r}
GRN.genes <- GRN$Gene.Name

BlastulaGRN <- subset(Blastula_temp_DEG_annot, common_name %in% GRN.genes)
# none.

# what about the whole annotation?

GRNs <- subset(annot.ortho.SPU, common_name %in% GRN.genes)
print(GRNs) 
# only 69 of these
# not sure if the names are all matching up correctly 
GRN.genes                  

GasturalaGRN <- subset(Gastrula_temp_DEG_annot, common_name %in% GRN.genes)        
# also none

```
