---
title: "EL-WGCNA"
author: "Maggie Schedl"
date: "7/21/2020"
output: html_document
---

```{r}
library(WGCNA)
library(tidyverse)
library(DESeq2)

```

# Data input and cleaning https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/Tutorials/Consensus-DataInput.pdf

Already have a counts file that is varience stabilizing transformed from the stage design from the DESeq2 analysis
That will be the input 

```{r}
# The following setting is important, do not omit.
options(stringsAsFactors = FALSE)

vst_s_counts <- read.table("vst_stage_counts.txt", sep = "\t")
# change names
colnames(vst_s_counts) <- c("29_4cell_rep_1" ,"29_4cell_rep_2" ,"29_4cell_rep_3", "29_blast_rep_1", "29_blast_rep_2" ,"29_blast_rep_3", "29_gast_rep_1",  "29_gast_rep_2",  "29_gast_rep_3", "29_larv_rep_1",  "29_larv_rep_2",  "29_larv_rep_3", "33_4cell_rep_1", "33_4cell_rep_2", "33_4cell_rep_3", "33_blast_rep_1", "33_blast_rep_2", "33_blast_rep_3", "33_gast_rep_1", "33_gast_rep_2",  "33_gast_rep_3",  "33_larv_rep_1",  "33_larv_rep_2",  "33_larv_rep_3", "eggs_rep_1" , "eggs_rep_2",  "eggs_rep_3")
head(vst_s_counts)
```

"each row corresponds to a gene and column to a
sample or auxiliary information"
```{r}
# check for genes with too many missing values 
gsg = goodSamplesGenes(vst_s_counts, verbose = 3)
gsg$allOK
# good!
```
Do not need to remove any samples to do the analysis

Need to subset these genes to a more managable number, 5000 is good (out of the 13296 in the full dataset), these should be the genes with the most varience (most signal!)

```{r}
matrix <- as.matrix(vst_s_counts) # make into a matrix so the vars fucntion will take it as an input and
vars <- rowVars(matrix) # apply the varience function to it to get the varience in each row
vars <- as.data.frame(vars) # change varience into data frame
vst_counts <- as.data.frame(matrix) # turn the counts data back into a dataframe
vst_s_counts$Genes <- rownames(vst_s_counts) # create a new column in the original dataframe that makes the row names an actual column
rownames(vars) <- vst_s_counts$Names # use that column as the template for the rownames of the vars dataframe
vst_counts_var <- cbind(vst_counts, vars) #add the row varience to the counts dataframe , binds by having the same rownames
vst_counts_var <- vst_counts_var[order(-vars),] # order this dataframe by the varience column and in decreasing order, so highest varience should be first
orderedvst_counts_var <- head(vst_counts_var, 5000) # then only take the top 5000 amount for a scaled down dataset
orderedvst_counts_var$vars <- NULL #remove the last column because it's not needed anymore
torderedvst_counts_var <- as.data.frame(t(as.matrix(orderedvst_counts_var))) #transpose to right format where samples are rows 
head(torderedvst_counts_var)
```


# Exploratory sample clustering

```{r}
sampleTree = hclust(dist(torderedvst_counts_var), method = "average")
# Plot the sample tree: Open a graphic output window of size 12 by 9 inches
# The user should change the dimensions if the window is too large or too small.
sizeGrWindow(12,9)
#pdf(file = "Plots/sampleClustering.pdf", width = 12, height = 9)
par(cex = 0.6)
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
```
There are no ovbsious outliers but they completely cluster by stage except for 4 cells and eggs. There is also the large break between early and later development

I might need to split the dataset between those two big groups 


# Step by step network construction https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/Tutorials/Consensus-NetworkConstruction-man.pdf

Choosing the soft-thresholding power: analysis of network topology

"Constructing a weighted gene network entails the choice of the soft thresholding power β to which co-expression
similarity is raised to calculate adjacency"


```{r}
powers = c(c(1:10), seq(from = 12, to=30, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(torderedvst_counts_var, powerVector = powers, verbose = 5, networkType = "signed") #make sure to specify network type
# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.80,col="blue")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
```

This is not how the scale independence graph should look, I need a singed R^2 above 0.8 and below 30 for the power
I want to do a signed network. 
"If the scale-free topology fit index fails to reach values above 0.8 for reasonable powers (less than 15 for unsigned or signed hybrid networks, and less than 30 for signed networks) and the mean connectivity remains relatively high (in the hundreds or above), chances are that the data exhibit a strong driver that makes a subset of the samples globally different from the rest. The difference causes high correlation among large groups of genes which invalidates the assumption of the scale-free topology approximation."https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/faq.html


I could change the way I normalized the data, try a TMM normalization, or I could subset the data into the two major groups. 

I think I will try subsetting first?

Select out rows in dataframe with only 4cell and egg samples

```{r}
# need the first 3, a middle 3 and the last 3

fourcell1 <- torderedvst_counts_var[1:3,]
fourcell2 <- torderedvst_counts_var[13:15,]
eggs <- torderedvst_counts_var[25:27,]
earlydevcounts <- rbind(eggs, fourcell1, fourcell2)

```

I am worried now though that this may be too few samples..


Select out rows in dataframe with blastula, gastrula, and larvae

```{r}
latedevcounts1 <- torderedvst_counts_var[4:12,]
latedevcounts12 <- torderedvst_counts_var[16:24,]
latedevcounts <- rbind(latedevcounts1, latedevcounts12)
```



Try picking soft thresholding power again 

early development 
```{r}
powers = c(c(1:10), seq(from = 12, to=30, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(earlydevcounts, powerVector = powers, verbose = 5, networkType = "signed") #make sure to specify network type
# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.80,col="blue")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
```
This still does not look good. I don't know why there is the v shape in the scale independence. It partly could have to do with the smaller number of samples. To accurately run the program it has to look like the one below



later development 
```{r}
powers = c(c(1:10), seq(from = 12, to=30, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(latedevcounts, powerVector = powers, verbose = 5, networkType = "signed") #make sure to specify network type
# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.80,col="blue")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
```
This one looks really great! power 10 has an R^2 of 0.9150 

I will go forward with only the late development samples I suppose. 


creating the network adjacency matrix, using the power picked and specifying the sign. The adjacency matrix is for all samples and is between each gene.

```{r}
vsoftPower = 10 # seting the soft power to 10 
vadjacency = adjacency(latedevcounts, power = vsoftPower, type= "signed")
```

Create topological overlap matrix from adjacency matrix
```{r}
# Turn adjacency into topological overlap
vTOM = TOMsimilarity(vadjacency)
vdissTOM = 1-vTOM # this is the dissimilarity, which is 1 minus the similarity
```

hierarchical clustering tree (dendrogram) of genes

```{r}
# Call the hierarchical clustering function
vgeneTree = hclust(as.dist(vdissTOM), method = "average")

# Average linkage: average the dissimilarities between all objects
#single (minimum dissimilarity) and complete (maximum dissimilarity) are other options, but seem too harsh

# Plot the resulting clustering tree (dendrogram)
sizeGrWindow(12,9)
plot(vgeneTree, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",
labels = FALSE, hang = 0.04)

```
Each one of the lines on this are genes. "Branches of the dendrogram group together densely interconnected, highly co-expressed genes." Now I need to cut the branches into coexpression modules 

These are "dynamically" cut because no specific height works for each individual branch 
"DeepSplit controls how finely the branches should be split. Higher values give more smaller modules, low values (0) give fewer larger modules"
```{r}
# chose a number of genes to be the minium in a module, the tutorial said 30 as an example
minModuleSize = 30; #must have 30 genes in it to be a module
# Module identification using dynamic tree cut:
vdynamicMods = cutreeDynamic(dendro = vgeneTree, distM = vdissTOM,
deepSplit = 2, pamRespectsDendro = FALSE, # deep split set at 2, might want to change...
minClusterSize = minModuleSize)
table(vdynamicMods)
```
This gives 14 co-expression modules

Visualize modules on the tree
```{r}
# Convert numeric lables into colors
vdynamicColors = labels2colors(vdynamicMods)
table(vdynamicColors)
# Plot the dendrogram and colors underneath
sizeGrWindow(8,6)
plotDendroAndColors(vgeneTree, vdynamicColors, "Dynamic Tree Cut",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
main = "Gene dendrogram and module colors")
```

Some modules my need to be collapsed into each other if they are also co-expressed. "The Dynamic Tree Cut may identify modules whose expression profiles are very similar. It may be prudent to merge such modules since their genes are highly co-expressed. To quantify co-expression similarity of entire modules, we calculate their eigengenes and cluster them on their correlation:"

```{r}
# Calculate eigengenes
vMEList = moduleEigengenes(latedevcounts, colors = vdynamicColors, trapErrors = FALSE, excludeGrey = TRUE)
vMEs = vMEList$eigengenes
# Calculate dissimilarity of module eigengenes
vMEDiss = 1-cor(vMEs);
# Cluster module eigengenes
vMETree = hclust(as.dist(vMEDiss), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(vMETree, main = "Clustering of module eigengenes",
xlab = "", sub = "")
```
This is how the modules cluser. 

```{r}
vMEList = moduleEigengenes(latedevcounts, colors = vdynamicColors, trapErrors = FALSE, excludeGrey = TRUE)
vMEs = vMEList$eigengenes
# Calculate dissimilarity of module eigengenes
vMEDiss = 1-cor(vMEs);
# Cluster module eigengenes
vMETree = hclust(as.dist(vMEDiss), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(vMETree, main = "Clustering of module eigengenes",
xlab = "", sub = "")
vMEDissThres = 0.15 # this means to merge modlues if they 85% correlated to eachother 
# Plot the cut line into the dendrogram
abline(h=vMEDissThres, col = "red")
# Call an automatic merging function
vmerge = mergeCloseModules(latedevcounts, vdynamicColors, cutHeight = vMEDissThres, verbose = 3)
# The merged module colors
vmergedColors = vmerge$colors
# Eigengenes of the new merged modules:
vmergedMEs = vmerge$newMEs
```
This would mean 2 modules are merged together

```{r}
sizeGrWindow(12, 9)
#pdf(file = "Plots/geneDendro-3.pdf", wi = 9, he = 6)
plotDendroAndColors(vgeneTree, cbind(vdynamicColors, vmergedColors),
c("Dynamic Tree Cut", "Merged dynamic"),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)

```

# Relating modules to stage and temp treatment information

Changed the treatment/trait information into numbers 
```{r}
Traitdat <- as.data.frame(read.csv("el-treatment-data.csv"))
head(Traitdat)
Traitdat2 <- Traitdat[,-1] #make column 1 into row names
rownames(Traitdat2) <- Traitdat[,1]
print(Traitdat2)

```

Think I need to subset again by only the rows that are for the later stages

```{r}
Trait1 <- Traitdat2[4:12,]
Trait2 <- Traitdat2[16:24,]
Traitdat3 <- rbind(Trait1, Trait2)
print(Traitdat3)
```

```{r}
#set up for using the module colors in further code
# Rename to moduleColors
vmoduleColors = vmergedColors
# Construct numerical labels corresponding to the colors
colorOrder = c("grey", standardColors(50))
vmoduleLabels = match(vmoduleColors, colorOrder)-1
vMEs = vmergedMEs
```

"Robust correlation. The default correlation method in all functions in WGCNA is standard Pearson correlation. In general, unless there is good reason to believe that there are no outlier measurements, we recommend (and use ourselves) the biweight mid-correlation as a robust alternative. This is implemented in WGCNA function bicor. Many WGCNA functions take the argument corFnc that allows one to specify an alternative correlation function to the standard cor and bicor is one option. Additional arguments to the correlation function can be specified using the argument corOptions (depending on function, this argument may require one of two alternate forms, please see the help for each function for details). In certain functions, notably the of the blockwise family, correlation function cannot be specified directly as a function; rather, one must use the argument corType to specify either Pearson or biweight mid-correlation."

I think I want to use the robust correlation method. However the temp treatment is bianary but the stage treatment is not "Dealing with binary data. When relating high-throughput data x to binary variable y such as sample traits, one can use argument robustY = FALSE to turn off the robust treatment for the y argment of bicor. This results in a hybrid robust-Pearson correlation as described in Langfelder and Horvath (2011)" 

"The options robustX, robustY allow the user to revert the calculation to standard correlation calculation. This is important, for example, if any of the variables is binary (or, more generally, discrete) as in such cases the robust methods produce meaningless results" 


```{r}
# Define numbers of genes and samples
vnGenes = ncol(latedevcounts);
vnSamples = nrow(latedevcounts);
# Recalculate MEs with color labels
vMEs0 = moduleEigengenes(latedevcounts, vmoduleColors)$eigengenes
vMEs = orderMEs(vMEs0)
vmoduleTraitCor = bicor(vMEs, Traitdat3, robustX = TRUE, robustY = FALSE, use = "all.obs"); #try pearson robust correlation
vmoduleTraitPvalue = corPvalueStudent(vmoduleTraitCor, vnSamples)
```

Visualize

```{r}
sizeGrWindow(10,6)
# Will display correlations and their p-values
vtextMatrix = paste(signif(vmoduleTraitCor, 2), "\n(",
signif(vmoduleTraitPvalue, 1), ")", sep = "");
dim(vtextMatrix) = dim(vmoduleTraitCor)
par(mar = c(6, 8.5, 3, 3));
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = vmoduleTraitCor,
xLabels = names(Traitdat2),
yLabels = names(vMEs),
ySymbols = names(vMEs),
colorLabels = FALSE,
colors = blueWhiteRed(50),
textMatrix = vtextMatrix,
setStdMargins = FALSE,
cex.text = 0.5,
zlim = c(-1,1),
main = paste("Module-trait relationships"))

```

The turquoise module is highly positively correlated with the stage. The yellow module is highly negatively correlated with the stage. There are a couple other singificant ones. There aren't any serious correlations with temperature but the green yellow module is slight (but not significant 0.1)

I am not sure what the negative correlation means exactly. 





I could potentially analyze all of the stages in one https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/faq.html
"Lack of scale-free topology fit by itself does not invalidate the data, but should be looked into carefully. It always helps to plot the sample clustering tree and any technical or biological sample information below it as in Figure 2 of Tutorial I, section 1; strong clusters in the clustering tree indicate globally different groups of samples. It could be the result a technical effect such as a batch effect, biological heterogeneity (e.g., a data set consisting of samples from 2 different tissues), or strong changes between conditions (say in a time series). One should investigate carefully whether there is sample heterogeneity, what drives the heterogeneity, and whether the data should be adjusted (see previous point).

If the lack of scale-free topology fit turns out to be caused by an interesting biological variable that one does not want to remove (i.e., adjust the data for), the appropriate soft-thresholding power can be chosen based on the number of samples as in the table below. This table has been updated in December 2017 to make the resulting networks conservative."


I would say that stage is like a time series, and clustering is probably the main reason there isn't scale free topology, which is an interesting biological variable. So I potentially could keep going with the full dataset and just use the acceptable soft threshold power for a signed network of 16. 




